Explaining Black-Box Models through Counterfactuals

### 2023-11-16 examples/CounterfactualExplanations.jl/paper.tex
this seems to work

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% Keywords command
\providecommand{\JCONkeywords}[1]
{
  \small	
  \section*{Keywords} #1
}
\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Explaining Black-Box Models through Counterfactuals},
  pdfkeywords={Julia, Explainable Artificial
Intelligence, Counterfactual Explanations, Algorithmic Recourse},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi

\setstretch{1}
\hypertarget{sec-intro}{%
\section{Introduction}\label{sec-intro}}

@@

\hypertarget{sec-related}{%
\section{Background and related work}\label{sec-related}}

@@

\hypertarget{literature-on-explainable-ai}{%
\subsection{Literature on Explainable
AI}\label{literature-on-explainable-ai}}

@@

\hypertarget{sec-method}{%
\subsection{A framework for Counterfactual
Explanations}\label{sec-method}}

@@

\begin{equation}\protect\hypertarget{eq-obj}{}{
\min_{x^\prime \in \mathcal{X}} h(x^\prime) \ \ \ \mbox{s. t.} \ \ \ M(x^\prime) = t
}\label{eq-obj}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-solution}{}{
x^\prime = \arg \min_{x^\prime}  \ell(M(x^\prime),t) + \lambda h(x^\prime)
}\label{eq-solution}\end{equation}

@@

\hypertarget{existing-software}{%
\subsection{Existing software}\label{existing-software}}

@@

\hypertarget{sec-arch}{%
\section{\texorpdfstring{Introducing:
\texttt{CounterfactualExplanations.jl}}{Introducing: CounterfactualExplanations.jl}}\label{sec-arch}}

@@

{\centering \includegraphics[width=3.33333in,height=2.38095in]{www/pkg_architecture.png}

@@

\end{figure}

\hypertarget{models}{%
\subsection{Models}\label{models}}

@@

\hypertarget{sec-gen}{%
\subsection{Generators}\label{sec-gen}}

@@

\hypertarget{tbl-gen}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{\label{tbl-gen}Overview of implemented counterfactual
generators.}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Generator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Model Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Search Space
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Composable
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Generator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Model Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Search Space
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Composable
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
ClaPROAR (Altmeyer et al. 2023) & gradient based & feature & yes \\
CLUE (Antorán et al. 2020) & gradient based & latent & yes \\
DiCE (Mothilal, Sharma, and Tan 2020) & gradient based & feature &
yes \\
FeatureTweak (Tolomei et al. 2017) & tree based & feature & no \\
Gravitational (Altmeyer et al. 2023) & gradient based & feature & yes \\
Greedy (Schut et al. 2021) & gradient based & feature & yes \\
GrowingSpheres (Laugel et al. 2017) & agnostic & feature & no \\
PROBE (Pawelczyk et al. 2022) & gradient based & feature & no \\
REVISE (Joshi et al. 2019) & gradient based & latent & yes \\
Wachter (Wachter, Mittelstadt, and Russell 2017) & gradient based &
feature & yes \\
\end{longtable}

@@

\hypertarget{data-catalogue}{%
\subsection{Data Catalogue}\label{data-catalogue}}

@@

\hypertarget{plotting}{%
\subsection{Plotting}\label{plotting}}

@@

\hypertarget{sec-use}{%
\section{Basic Usage}\label{sec-use}}

@@

\hypertarget{sec-simple}{%
\subsection{A Simple Generic Generator}\label{sec-simple}}

@@

{\centering \includegraphics[width=3.33333in,height=2.5in]{www/ce_binary.png}

@@

\end{figure}

@@

\hypertarget{sec-gen-comp}{%
\subsection{Composing Generators}\label{sec-gen-comp}}

@@

\begin{equation}\protect\hypertarget{eq-comp}{}{
\mathbf{Z}^\prime = \arg \min_{\mathbf{Z}^\prime \in \mathcal{Z}^{L \times K}} \{  {\ell(M(f(\mathbf{Z}^\prime)),t)} + \lambda \cdot {\text{diversity}(f(\mathbf{Z}^\prime)) }  \} 
}\label{eq-comp}\end{equation}

@@

{\centering \includegraphics[width=3.33333in,height=2.5in]{www/binary_advanced.png}

@@

\end{figure}

\hypertarget{sec-mut}{%
\subsection{Mutability Constraints}\label{sec-mut}}

@@

{\centering \includegraphics[width=3.33333in,height=2.5in]{www/constraint_mutability.png}

@@

\end{figure}

\hypertarget{sec-eval}{%
\subsection{Evaluation and Benchmarking}\label{sec-eval}}

@@

{\centering \includegraphics[width=3.33333in,height=2.5in]{www/bmk.png}

@@

\end{figure}

\hypertarget{sec-custom}{%
\section{Customization and Extensibility}\label{sec-custom}}

@@

\hypertarget{sec-custom-mod}{%
\subsection{Adding Custom Models}\label{sec-custom-mod}}

@@

{\centering \includegraphics[width=3.33333in,height=2.5in]{www/ce_multi.png}

@@

\end{figure}

\hypertarget{sec-custom-gen}{%
\subsection{Adding Custom Generators}\label{sec-custom-gen}}

@@

\hypertarget{a-generator-with-dropout}{%
\subsubsection{A Generator with
Dropout}\label{a-generator-with-dropout}}

@@

{\centering \includegraphics[width=3.33333in,height=2.5in]{www/dropout.png}

@@

\end{figure}

\hypertarget{sec-emp}{%
\section{A Real-World Examples}\label{sec-emp}}

@@

\hypertarget{give-me-some-credit}{%
\subsection{Give Me Some Credit}\label{give-me-some-credit}}

@@

{\centering \includegraphics[width=3.33333in,height=1.33333in]{www/credit.png}

@@

\end{figure}

\hypertarget{mnist}{%
\subsection{MNIST}\label{mnist}}

@@

{\centering \includegraphics[width=3.33333in,height=1.11111in]{www/mnist_9to4_latent.png}

@@

\end{figure}

\hypertarget{sec-outlook}{%
\section{Discussion and Outlook}\label{sec-outlook}}

@@

\hypertarget{candidate-models-and-generators}{%
\subsection{Candidate models and
generators}\label{candidate-models-and-generators}}

@@

\hypertarget{additional-datasets}{%
\subsection{Additional datasets}\label{additional-datasets}}

@@

\hypertarget{sec-conclude}{%
\section{Concluding remarks}\label{sec-conclude}}

@@

\hypertarget{sec-ack}{%
\section{Acknowledgements}\label{sec-ack}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-altmeyer2023endogenous}{}}%
Altmeyer, Patrick, Giovan Angela, Aleksander Buszydlik, Karol Dobiczek,
Arie van Deursen, and Cynthia Liem. 2023. {``Endogenous {Macrodynamics}
in {Algorithmic} {Recourse}.''} In \emph{First {IEEE} {Conference} on
{Secure} and {Trustworthy} {Machine} {Learning}}.
\url{https://doi.org/10.1109/satml54575.2023.00036}.

\leavevmode\vadjust pre{\hypertarget{ref-antoran2020getting}{}}%
Antorán, Javier, Umang Bhatt, Tameem Adel, Adrian Weller, and José
Miguel Hernández-Lobato. 2020. {``Getting a Clue: {A} Method for
Explaining Uncertainty Estimates.''}
\url{https://arxiv.org/abs/2006.06848}.

\leavevmode\vadjust pre{\hypertarget{ref-arrieta2020explainable}{}}%
Arrieta, Alejandro Barredo, Natalia Diaz-Rodriguez, Javier Del Ser,
Adrien Bennetot, Siham Tabik, Alberto Barbado, Salvador Garcia, et al.
2020. {``Explainable {Artificial Intelligence} ({XAI}): {Concepts},
Taxonomies, Opportunities and Challenges Toward Responsible {AI}.''}
\emph{Information Fusion} 58: 82--115.
\url{https://doi.org/10.1016/j.inffus.2019.12.012}.

\leavevmode\vadjust pre{\hypertarget{ref-becker1996adult}{}}%
Barry Becker, Ronny Kohavi. 1996. {``Adult.''} UCI Machine Learning
Repository. \url{https://doi.org/10.24432/C5XW20}.

\leavevmode\vadjust pre{\hypertarget{ref-blaom2020mlj}{}}%
Blaom, Anthony D., Franz Kiraly, Thibaut Lienart, Yiannis Simillides,
Diego Arenas, and Sebastian J. Vollmer. 2020. {``{MLJ}: {A Julia}
Package for Composable Machine Learning.''} \emph{Journal of Open Source
Software} 5 (55): 2704. \url{https://doi.org/10.21105/joss.02704}.

\leavevmode\vadjust pre{\hypertarget{ref-borch2022machine}{}}%
Borch, Christian. 2022. {``Machine Learning, Knowledge Risk, and
Principal-Agent Problems in Automated Trading.''} \emph{Technology in
Society}, 101852. \url{https://doi.org/10.1016/j.techsoc.2021.101852}.

\leavevmode\vadjust pre{\hypertarget{ref-buolamwini2018gender}{}}%
Buolamwini, Joy, and Timnit Gebru. 2018. {``Gender Shades:
{Intersectional} Accuracy Disparities in Commercial Gender
Classification.''} In \emph{Conference on Fairness, Accountability and
Transparency}, 77--91. {PMLR}.

\leavevmode\vadjust pre{\hypertarget{ref-dandl2023counterfactuals}{}}%
Dandl, Susanne, Andreas Hofheinz, Martin Binder, Bernd Bischl, and
Giuseppe Casalicchio. 2023. {``Counterfactuals: {An} {R} {Package} for
{Counterfactual} {Explanation} {Methods}.''} arXiv.
\url{http://arxiv.org/abs/2304.06569}.

\leavevmode\vadjust pre{\hypertarget{ref-delaney2021uncertainty}{}}%
Delaney, Eoin, Derek Greene, and Mark T. Keane. 2021. {``Uncertainty
{Estimation} and {Out}-of-{Distribution} {Detection} for
{Counterfactual} {Explanations}: {Pitfalls} and {Solutions}.''} arXiv.
\url{http://arxiv.org/abs/2107.09734}.

\leavevmode\vadjust pre{\hypertarget{ref-fan2020interpretability}{}}%
Fan, Fenglei, Jinjun Xiong, and Ge Wang. 2020. {``On Interpretability of
Artificial Neural Networks.''} \url{https://arxiv.org/abs/2001.02522}.

\leavevmode\vadjust pre{\hypertarget{ref-goodfellow2014explaining}{}}%
Goodfellow, Ian J, Jonathon Shlens, and Christian Szegedy. 2014.
{``Explaining and Harnessing Adversarial Examples.''}
\url{https://arxiv.org/abs/1412.6572}.

\leavevmode\vadjust pre{\hypertarget{ref-hoffman1994german}{}}%
Hoffman, Hans. 1994. {``German {Credit Data}.''}
\url{https://archive.ics.uci.edu/ml/datasets/statlog+(german+credit+data)}.

\leavevmode\vadjust pre{\hypertarget{ref-innes2018flux}{}}%
Innes, Mike. 2018. {``Flux: {Elegant} Machine Learning with {Julia}.''}
\emph{Journal of Open Source Software} 3 (25): 602.
\url{https://doi.org/10.21105/joss.00602}.

\leavevmode\vadjust pre{\hypertarget{ref-joshi2019realistic}{}}%
Joshi, Shalmali, Oluwasanmi Koyejo, Warut Vijitbenjaronk, Been Kim, and
Joydeep Ghosh. 2019. {``Towards Realistic Individual Recourse and
Actionable Explanations in Black-Box Decision Making Systems.''}
\url{https://arxiv.org/abs/1907.09615}.

\leavevmode\vadjust pre{\hypertarget{ref-kaggle2011give}{}}%
Kaggle. 2011. {``Give Me Some Credit, {Improve} on the State of the Art
in Credit Scoring by Predicting the Probability That Somebody Will
Experience Financial Distress in the Next Two Years.''} {Kaggle}.
\url{https://www.kaggle.com/c/GiveMeSomeCredit}.

\leavevmode\vadjust pre{\hypertarget{ref-karimi2020survey}{}}%
Karimi, Amir-Hossein, Gilles Barthe, Bernhard Schölkopf, and Isabel
Valera. 2020. {``A Survey of Algorithmic Recourse: Definitions,
Formulations, Solutions, and Prospects.''}
\url{https://arxiv.org/abs/2010.04050}.

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% Keywords command
\providecommand{\JCONkeywords}[1]
{
  \small	
  \section*{Keywords} #1
}
\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Explaining Black-Box Models through Counterfactuals},
  pdfkeywords={Julia, Explainable Artificial
Intelligence, Counterfactual Explanations, Algorithmic Recourse},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\setstretch{1}
\section{Introduction}\label{sec-intro}

@@

\section{Background and related work}\label{sec-related}

@@

\subsection{Literature on Explainable
AI}\label{literature-on-explainable-ai}

@@

\subsection{A framework for Counterfactual
Explanations}\label{sec-method}

@@

\begin{equation}\phantomsection\label{eq-obj}{
\min_{x^\prime \in \mathcal{X}} h(x^\prime) \ \ \ \mbox{s. t.} \ \ \ M(x^\prime) = t
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-solution}{
x^\prime = \arg \min_{x^\prime}  \ell(M(x^\prime),t) + \lambda h(x^\prime)
}\end{equation}

@@

\subsection{Existing software}\label{existing-software}

@@

\section{\texorpdfstring{Introducing:
\texttt{CounterfactualExplanations.jl}}{Introducing: CounterfactualExplanations.jl}}\label{sec-arch}

@@

\centering{

\includegraphics[width=3.33333in,height=2.38095in]{www/pkg_architecture.png}

@@

\end{figure}%

\subsection{Models}\label{models}

@@

\subsection{Generators}\label{sec-gen}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{Overview of implemented counterfactual
generators.}\label{tbl-gen}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Generator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Model Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Search Space
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Composable
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Generator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Model Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Search Space
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Composable
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
ClaPROAR (Altmeyer et al. 2023) & gradient based & feature & yes \\
CLUE (Antorán et al. 2020) & gradient based & latent & yes \\
DiCE (Mothilal, Sharma, and Tan 2020) & gradient based & feature &
yes \\
FeatureTweak (Tolomei et al. 2017) & tree based & feature & no \\
Gravitational (Altmeyer et al. 2023) & gradient based & feature & yes \\
Greedy (Schut et al. 2021) & gradient based & feature & yes \\
GrowingSpheres (Laugel et al. 2017) & agnostic & feature & no \\
PROBE (Pawelczyk et al. 2022) & gradient based & feature & no \\
REVISE (Joshi et al. 2019) & gradient based & latent & yes \\
Wachter (Wachter, Mittelstadt, and Russell 2017) & gradient based &
feature & yes \\
\end{longtable}

@@

\subsection{Data Catalogue}\label{data-catalogue}

@@

\subsection{Plotting}\label{plotting}

@@

\section{Basic Usage}\label{sec-use}

@@

\subsection{A Simple Generic Generator}\label{sec-simple}

@@

\centering{

\includegraphics[width=3.33333in,height=2.5in]{www/ce_binary.png}

@@

\end{figure}%

@@

\subsection{Composing Generators}\label{sec-gen-comp}

@@

\begin{equation}\phantomsection\label{eq-comp}{
\mathbf{Z}^\prime = \arg \min_{\mathbf{Z}^\prime \in \mathcal{Z}^{L \times K}} \{  {\ell(M(f(\mathbf{Z}^\prime)),t)} + \lambda \cdot {\text{diversity}(f(\mathbf{Z}^\prime)) }  \} 
}\end{equation}

@@

\centering{

\includegraphics[width=3.33333in,height=2.5in]{www/binary_advanced.png}

@@

\end{figure}%

\subsection{Mutability Constraints}\label{sec-mut}

@@

\centering{

\includegraphics[width=3.33333in,height=2.5in]{www/constraint_mutability.png}

@@

\end{figure}%

\subsection{Evaluation and Benchmarking}\label{sec-eval}

@@

\centering{

\includegraphics[width=3.33333in,height=2.5in]{www/bmk.png}

@@

\end{figure}%

\section{Customization and Extensibility}\label{sec-custom}

@@

\subsection{Adding Custom Models}\label{sec-custom-mod}

@@

\centering{

\includegraphics[width=3.33333in,height=2.5in]{www/ce_multi.png}

@@

\end{figure}%

\subsection{Adding Custom Generators}\label{sec-custom-gen}

@@

\subsubsection{A Generator with Dropout}\label{a-generator-with-dropout}

@@

\centering{

\includegraphics[width=3.33333in,height=2.5in]{www/dropout.png}

@@

\end{figure}%

\section{A Real-World Examples}\label{sec-emp}

@@

\subsection{Give Me Some Credit}\label{give-me-some-credit}

@@

\centering{

\includegraphics[width=3.33333in,height=1.33333in]{www/credit.png}

@@

\end{figure}%

\subsection{MNIST}\label{mnist}

@@

\centering{

\includegraphics[width=3.33333in,height=1.11111in]{www/mnist_9to4_latent.png}

@@

\end{figure}%

\section{Discussion and Outlook}\label{sec-outlook}

@@

\subsection{Candidate models and
generators}\label{candidate-models-and-generators}

@@

\subsection{Additional datasets}\label{additional-datasets}

@@

\section{Concluding remarks}\label{sec-conclude}

@@

\section{Acknowledgements}\label{sec-ack}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-altmeyer2023endogenous}
Altmeyer, Patrick, Giovan Angela, Aleksander Buszydlik, Karol Dobiczek,
Arie van Deursen, and Cynthia Liem. 2023. {``Endogenous {Macrodynamics}
in {Algorithmic} {Recourse}.''} In \emph{First {IEEE} {Conference} on
{Secure} and {Trustworthy} {Machine} {Learning}}.
\url{https://doi.org/10.1109/satml54575.2023.00036}.

\bibitem[\citeproctext]{ref-antoran2020getting}
Antorán, Javier, Umang Bhatt, Tameem Adel, Adrian Weller, and José
Miguel Hernández-Lobato. 2020. {``Getting a Clue: {A} Method for
Explaining Uncertainty Estimates.''}
\url{https://arxiv.org/abs/2006.06848}.

\bibitem[\citeproctext]{ref-arrieta2020explainable}
Arrieta, Alejandro Barredo, Natalia Diaz-Rodriguez, Javier Del Ser,
Adrien Bennetot, Siham Tabik, Alberto Barbado, Salvador Garcia, et al.
2020. {``Explainable {Artificial Intelligence} ({XAI}): {Concepts},
Taxonomies, Opportunities and Challenges Toward Responsible {AI}.''}
\emph{Information Fusion} 58: 82--115.
\url{https://doi.org/10.1016/j.inffus.2019.12.012}.

\bibitem[\citeproctext]{ref-becker1996adult}
Barry Becker, Ronny Kohavi. 1996. {``Adult.''} UCI Machine Learning
Repository. \url{https://doi.org/10.24432/C5XW20}.

\bibitem[\citeproctext]{ref-blaom2020mlj}
Blaom, Anthony D., Franz Kiraly, Thibaut Lienart, Yiannis Simillides,
Diego Arenas, and Sebastian J. Vollmer. 2020. {``{MLJ}: {A Julia}
Package for Composable Machine Learning.''} \emph{Journal of Open Source
Software} 5 (55): 2704. \url{https://doi.org/10.21105/joss.02704}.

\bibitem[\citeproctext]{ref-borch2022machine}
Borch, Christian. 2022. {``Machine Learning, Knowledge Risk, and
Principal-Agent Problems in Automated Trading.''} \emph{Technology in
Society}, 101852. \url{https://doi.org/10.1016/j.techsoc.2021.101852}.

\bibitem[\citeproctext]{ref-buolamwini2018gender}
Buolamwini, Joy, and Timnit Gebru. 2018. {``Gender Shades:
{Intersectional} Accuracy Disparities in Commercial Gender
Classification.''} In \emph{Conference on Fairness, Accountability and
Transparency}, 77--91. {PMLR}.

\bibitem[\citeproctext]{ref-dandl2023counterfactuals}
Dandl, Susanne, Andreas Hofheinz, Martin Binder, Bernd Bischl, and
Giuseppe Casalicchio. 2023. {``Counterfactuals: {An} {R} {Package} for
{Counterfactual} {Explanation} {Methods}.''} arXiv.
\url{http://arxiv.org/abs/2304.06569}.

\bibitem[\citeproctext]{ref-delaney2021uncertainty}
Delaney, Eoin, Derek Greene, and Mark T. Keane. 2021. {``Uncertainty
{Estimation} and {Out}-of-{Distribution} {Detection} for
{Counterfactual} {Explanations}: {Pitfalls} and {Solutions}.''} arXiv.
\url{http://arxiv.org/abs/2107.09734}.

\bibitem[\citeproctext]{ref-fan2020interpretability}
Fan, Fenglei, Jinjun Xiong, and Ge Wang. 2020. {``On Interpretability of
Artificial Neural Networks.''} \url{https://arxiv.org/abs/2001.02522}.

\bibitem[\citeproctext]{ref-goodfellow2014explaining}
Goodfellow, Ian J, Jonathon Shlens, and Christian Szegedy. 2014.
{``Explaining and Harnessing Adversarial Examples.''}
\url{https://arxiv.org/abs/1412.6572}.

\bibitem[\citeproctext]{ref-hoffman1994german}
Hoffman, Hans. 1994. {``German {Credit Data}.''}
\url{https://archive.ics.uci.edu/ml/datasets/statlog+(german+credit+data)}.

\bibitem[\citeproctext]{ref-innes2018flux}
Innes, Mike. 2018. {``Flux: {Elegant} Machine Learning with {Julia}.''}
\emph{Journal of Open Source Software} 3 (25): 602.
\url{https://doi.org/10.21105/joss.00602}.

\bibitem[\citeproctext]{ref-joshi2019realistic}
Joshi, Shalmali, Oluwasanmi Koyejo, Warut Vijitbenjaronk, Been Kim, and
Joydeep Ghosh. 2019. {``Towards Realistic Individual Recourse and
Actionable Explanations in Black-Box Decision Making Systems.''}
\url{https://arxiv.org/abs/1907.09615}.

\bibitem[\citeproctext]{ref-kaggle2011give}
Kaggle. 2011. {``Give Me Some Credit, {Improve} on the State of the Art
in Credit Scoring by Predicting the Probability That Somebody Will
Experience Financial Distress in the Next Two Years.''} {Kaggle}.
\url{https://www.kaggle.com/c/GiveMeSomeCredit}.

\bibitem[\citeproctext]{ref-karimi2020survey}
Karimi, Amir-Hossein, Gilles Barthe, Bernhard Schölkopf, and Isabel
Valera. 2020. {``A Survey of Algorithmic Recourse: Definitions,
Formulations, Solutions, and Prospects.''}
\url{https://arxiv.org/abs/2010.04050}.

\bibitem[\citeproctext]{ref-karimi2021algorithmic}
Karimi, Amir-Hossein, Bernhard Schölkopf, and Isabel Valera. 2021.
{``Algorithmic Recourse: From Counterfactual Explanations to
Interventions.''} In \emph{Proceedings of the 2021 {ACM Conference} on
{Fairness}, {Accountability}, and {Transparency}}, 353--62.
